Supp mat: time series paper

### 2017-06-05 writing/supp_mat_draft.Rmd
edited supp mat to include cleaned data

```{r, echo=F, fig.cap='Example of calculating minimum time required for growth rate estimation. (a) abundance over time, (b) mean and standard deviation of growth rate for subsamples of entire time series, and (c) the percent error between mean estimated growth rate and the true longterm growth rate. The vertical bar denotes the minimum time required to estimate growth rate within 10% error.\\label{fig:growth_rate}'}
#Example of using population growth rate instead of power
setwd("/Users/eastonwhite/Desktop/Research/time-series-project")
source("scripts/calculate_geometric_growth.R")
load('cleaned-data/pop_info_example_goodNAs.Rdata')

@@

```{r, echo=F,fig.cap='Histogram of the minimum time required in order to estimate the longterm growth rate within 20% error.\\label{fig:min_time_growth_dist}'}
# Growth rates calculations for each species
setwd("/Users/eastonwhite/Desktop/Research/time-series-project")
load('cleaned-data/pop_info_example_goodNAs.Rdata')

@@

```{r,echo=F,fig.cap='results here from GAM.\\label{fig:gam_result}'}
# show gam results for minimium time required
setwd("/Users/eastonwhite/Desktop/Research/time-series-project")
load('cleaned-data/pop_info_example_goodNAs.Rdata')

>>>>

```{r, echo=F, fig.cap='Example of calculating minimum time required for growth rate estimation. (a) abundance over time, (b) mean and standard deviation of growth rate for subsamples of entire time series, and (c) the percent error between mean estimated growth rate and the true longterm growth rate. The vertical bar denotes the minimum time required to estimate growth rate within 10% error.\\label{fig:growth_rate}'}
#Example of using population growth rate instead of power
setwd("/Users/eastonwhite/Desktop/Research/time-series-project")
source("scripts/calculate_geometric_growth.R")
load('cleaned-data/cleaned_timeseries_database.Rdata')

@@

```{r, echo=F,fig.cap='Histogram of the minimum time required in order to estimate the longterm growth rate within 20% error.\\label{fig:min_time_growth_dist}'}
# Growth rates calculations for each species
setwd("/Users/eastonwhite/Desktop/Research/time-series-project")
load('cleaned-data/cleaned_timeseries_database.Rdata')

@@

```{r,echo=F,fig.cap='results here from GAM.\\label{fig:gam_result}'}
# show gam results for minimium time required
setwd("/Users/eastonwhite/Desktop/Research/time-series-project")
load('cleaned-data/cleaned_timeseries_database.Rdata')
